Stat 400 Project

### 2021-12-04 Stat 400 proj.Rmd
Need to fix infection status error

  #Create null incubation and recovery time columns
  #inc_time <- rep(NA, num_subjects)
  #rec_time <- rep(NA, num_subjects)

@@

  #Put into a data frame
  df <- as.data.frame(cbind(as.numeric(start_x), as.numeric(start_y), subjects,recovery_days,inc_time))
  colnames(df)[1] <- 'x'
  colnames(df)[2] <- 'y'
  colnames(df)[3] <- 'subjects'
  colnames(df)[4] <- 'incubation'
  colnames(df)[5] <- 'recovery'
  return(df)
}

@@

#Function for deciding if infections occurred
#BUG -- If the mean_crit_dist is small, all infections go away!!

#t = the current day, rt is df of recovery times. 
infection_status <- function(state, mean_crit_dist){

@@

  for(i in 1:nrow(current_infected)){
    for(j in 1:nrow(current_non_infected)){
      x_i <- as.numeric(current_infected[i, 'x'])
      y_i <- as.numeric(current_infected[i, 'y'])
      x_s <- as.numeric(current_suceptable[j, 'x'])
      y_s <- as.numeric(current_suceptable[j, 'y'])

      crucial_distance <- rexp(1, 1/mean_crit_dist)
      d <- sqrt((x_i - x_s)^2 + (y_i - y_s)^2)

      if(d <= crucial_distance){
        newly_infected <- c(newly_infected, j)
      }
    }
  }
  current_non_infected[newly_infected, 3] <- 'I'
  current_non_infected[newly_infected, 4] <- rpois(n=length(newly_infected), lambda = 5)
  current_non_infected[newly_infected, 5] <- rpois(n=length(newly_infected), lambda = 14)
  new_state <- rbind(current_infected, current_non_infected)
  return(new_state)
}

@@

  recovery_time <- initial_data[,4]

@@

      updated_positions <- update_coords(initial_data, change)
      checked_positions <- coord_checker(og_df=initial_data, new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
      new_status <- infection_status(checked_positions, 2)

      not_recovered = new_status[new_status[,5]>=0]
      other = new_status[new_status[,5]<0]

      new_status = rbind(non_recovered[,5]-1,other)

      end_day[[i]] <- new_status

@@

      updated_positions <- update_coords(end_day[[i-1]], change)
      checked_positions <- coord_checker(og_df=end_day[[i-1]], new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
      new_status <- infection_status(checked_positions, 1/5)

      not_recovered = new_status[new_status[,5]>=0]
      other = new_status[new_status[,5]<0]

      new_status = rbind(non_recovered[,5]-1,other)

      end_day[[i]] <- new_status

>>>>

@@

  #Put into a data frame
  df <- as.data.frame(cbind(as.numeric(start_x), as.numeric(start_y), subjects, rec_days, inc_time))
  colnames(df)[1] <- 'x'
  colnames(df)[2] <- 'y'
  colnames(df)[3] <- 'subjects'
  colnames(df)[4] <- 'incubation'
  colnames(df)[5] <- 'recovery'
  return(df)
}

@@

#Function for deciding if infections occurred
#BUG -- If the mean_crit_dist is small, all infections go away!!
infection_status <- function(state, mean_crit_dist){

@@

  for(i in 1:nrow(current_infected)){
    for(j in 1:nrow(current_non_infected)){
      x_i <- as.numeric(current_infected[i, 'x'])
      y_i <- as.numeric(current_infected[i, 'y'])
      x_s <- as.numeric(current_non_infected[j, 'x'])
      y_s <- as.numeric(current_non_infected[j, 'y'])

      crucial_distance <- rexp(1, 1/mean_crit_dist)
      d <- sqrt((x_i - x_s)^2 + (y_i - y_s)^2)
      print(c(d <= crucial_distance, x_i, x_s))
      if(d <= crucial_distance){
        newly_infected <- c(newly_infected, j)
      }

    }
  }
  current_non_infected[newly_infected, 3] <- 'I'
  #Give incubation time
  current_non_infected[newly_infected, 4] <- rpois(n=length(newly_infected), lambda = 5)
  #Give recovery time
  current_non_infected[newly_infected, 5] <- rpois(n=length(newly_infected), lambda = 14)

  new_state <- rbind(current_infected, current_non_infected)
  return(new_state)
}

@@

@@

      updated_positions <- update_coords(initial_data, change)
      checked_positions <- coord_checker(og_df=initial_data, new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
      print(checked_positions)
      new_status <- infection_status(checked_positions, 2)

      not_recovered = new_status[new_status[, 5] > 0]
      new_time <- not_recovered[, 5] - 1
      not_recovered[, 5] <- new_time
      infected_0 <- new_status[new_status[, 5] == 0]
      infected_0[, 3] <- 'R'
      not_infected = new_status[new_status[, 5] < 0]

      new_status = rbind(not_recovered, infected_0, not_infected)
      end_day[[i]] <- new_status

@@

      updated_positions <- update_coords(end_day[[i-1]], change)
      checked_positions <- coord_checker(og_df=end_day[[i-1]], new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
      new_status <- infection_status(checked_positions, 5)

      not_recovered = new_status[new_status[, 5] > 0]
      new_time <- not_recovered[, 5] - 1
      not_recovered[, 5] <- new_time
      infected_0 <- new_status[new_status[, 5] == 0]
      infected_0[, 3] <- 'R'
      not_infected = new_status[new_status[, 5] < 0]

      new_status = rbind(not_recovered, infected_0, not_infected)
      end_day[[i]] <- new_status
